Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2020-08-02 article_springer/article_springer.Rmd

---
title: "Statistical Inference for inter-arrival times of extreme events in bursty time series"
# titlerunning: "CTRE: POT for Bursty Time Series"
thanks: |
    Peter Straka was supported by the 
    Discovery Early Career Research Award DE160101147 on the Project 
    "Predicting Extremes when Events Occur in Bursts" by the Australian
    Research Council.
    Katharina Hees was supported by 
    the DAAD co-financed by the German Federal Ministry of Education and 
    Research (BMBF).

@@

: If $\beta = 1$, the result of the Theorem above is standard, see  
Equation (2.2) in @Gut1999. In @Anderson1987  a similar result is shown with a different choice of scaling constant. [@MeerschaertStoev08] proved a limit theorem for the maxima of iid random variables separated by infinite mean waiting times. They have also shown that the hitting time of the limit process is Mittag-Leffler distributed. [@Basrak2014] described the asymptotic distribution, under similar assumptions, of all upper orders statistics using point processes.

@@

The authors would like to thank Prof. Peter Scheffler for insights on 
stochastic process limits for CTRMs, Prof. Roland Fried for discussion 
regarding the statistical methods and Gurtek Gill who helped create the 
MittagLeffleR R-package. Peter Straka was supported by the Discovery 
Early Career Research Award DE160101147 on the Project 
“Predicting Extremes when Events Occurin Bursts” by 
the Australian Research Council. Katharina Hees was 
supported by the DAAD co-financed by the 
German Federal Ministry of Education and Research (BMBF).

>>>>

---
title: "Statistical Inference for inter-arrival times of extreme events in bursty time series"
# titlerunning: "CTRE: POT for Bursty Time Series"

@@

: If $\beta = 1$, the result of the Theorem above is standard, see
Equation (2.2) in @Gut1999. In @Anderson1987  a similar result is shown with a different choice of scaling constant. @MeerschaertStoev08 proved a limit theorem for the maxima of iid random variables separated by infinite mean waiting times. They also show that the hitting time of the limit process is Mittag-Leffler distributed. @Basrak2014 describe the asymptotic distribution, under similar assumptions, of all upper orders statistics of the maximum process using point processes.

@@

Peter Straka was supported by the Discovery 
Early Career Research Award DE160101147 on the Project 
“Predicting Extremes when Events Occurin Bursts” by 
the Australian Research Council. Katharina Hees was 
supported by the DAAD co-financed by the 
German Federal Ministry of Education and Research (BMBF).
The authors would like to thank Prof. Peter Scheffler for insights on 
stochastic process limits for CTRMs, Prof. Roland Fried for discussion 
regarding the statistical methods and Gurtek Gill who helped create the 
MittagLeffleR R-package.
